Summary Tables

### 2021-08-11 summary_tables.Rmd
Changing the label of causes in health outcomes and Regen

### Change in deaths due to disease {#change_death_disease}
```{r}
disease_totals <- lapply(io[-2],function(x){
  xx <- x$outcomes$hb$deaths
  xxx <- sapply(1:5,function(y){
    colSums(xx[, seq(y + 2, ncol(xx), by = 5)])
  })
  colnames(xxx) <- scen_names
  rownames(xxx) <- sapply(rownames(xxx), function(y) gsub('scen1_', '', y))
  xxx
})
sum_and_round_and_print(disease_totals,"Change in deaths due to disease in ")
```

@@

### Change in YLL due to disease {#change_yll_disease}
```{r}
disease_totals <- lapply(io[-2],function(x){
  xx <- x$outcomes$hb$ylls
  xxx <- sapply(1:5,function(y) {
    colSums(xx[,seq(y + 2, ncol(xx), by = 5)])
  })
  colnames(xxx) <- scen_names
  rownames(xxx) <- sapply(rownames(xxx), function(y) gsub('scen1_','',y))
  xxx
})
sum_and_round_and_print(disease_totals,"Change in YLL due to disease in ")
```

>>>>

### Change in deaths due to disease {#change_death_disease}
```{r}
disease_totals <- lapply(io[-2],function(x){
  xx <- x$outcomes$hb$deaths
  xxx <- sapply(1:5,function(y){
    colSums(xx[, seq(y + 2, ncol(xx), by = 5)])
  })
  colnames(xxx) <- scen_names
  #rownames(xxx) <- sapply(rownames(xxx), function(y) gsub('scen1_', '', y))
  rownames(xxx) <- c("PA_AllCauses", "PA_AP_IschemicHeartDisease", "PA_Neoplasms",
                     "PA_AP_LungCancer", "AP_COPD", "PA_AP_Stroke",
                     "PA_AP_T2Diabetes", "AP_LowerRespiratoryInfections",
                     "PA_BreastCancer", "PA_ColonCancer", "PA_UterineCancer",
                     "Injuries")
  xxx
})
sum_and_round_and_print(disease_totals,"Change in deaths due to disease in ")
```

@@

### Change in YLL due to disease {#change_yll_disease}
```{r}
disease_totals <- lapply(io[-2],function(x){
  xx <- x$outcomes$hb$ylls
  xxx <- sapply(1:5,function(y) {
    colSums(xx[,seq(y + 2, ncol(xx), by = 5)])
  })
  colnames(xxx) <- scen_names
  #rownames(xxx) <- sapply(rownames(xxx), function(y) gsub('scen1_','',y))
  rownames(xxx) <- c("PA_AllCauses", "PA_AP_IschemicHeartDisease", "PA_Neoplasms",
                     "PA_AP_LungCancer", "AP_COPD", "PA_AP_Stroke",
                     "PA_AP_T2Diabetes", "AP_LowerRespiratoryInfections",
                     "PA_BreastCancer", "PA_ColonCancer", "PA_UterineCancer",
                     "Injuries")
  xxx
})
sum_and_round_and_print(disease_totals,"Change in YLL due to disease in ")
```
